A survey of HTTP caching implementations on the open Semantic Web

### 2015-03-12 sanity/paper1.tex
Move TODOs
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1075 43ef1190-90fd-4dd7-a769-d0121f02b80e

This results in an NQuads file per host, which is then loaded into a
Virtuoso-based SPARQL endpoint for analysis by using the statistics
system R\cite{kn:r} in the following section.\todo{Reorg, rev 6}

@@

In Figure~\ref{fig:hardall}, there is a barplot where
the freshness lifetime is grouped in bins. We see that in these
categories, the most common is to prohibit caching. Nevertheless, many
also declare a standards compliant freshness lifetime in minutes to
days\todo{qqplot in report}.

>>>>

This results in an NQuads file per host, which is then loaded into a
Virtuoso-based SPARQL endpoint for analysis by using the statistics
system R\cite{kn:r} in the following section.

@@

In Figure~\ref{fig:hardall}, there is a barplot where
the freshness lifetime is grouped in bins. We see that in these
categories, the most common is to prohibit caching. Nevertheless, many
also declare a standards compliant freshness lifetime in minutes to
days.
